% !TEX program = xelatex
\providecommand{\IfDocumentMetadataT}[1]{}

\documentclass[letterpaper]{resume_config}


\begin{document}

\Header
    {Shubham Mathur}
    {+91-9443129941}
    {shubham.mathur.wrk@gmail.com}
    {shubham-mathur-biz}
    {https://googleknight.github.io/}
    {googleknight}

\section{\textcolor{NavyBlue}{Work Experience}}

\WorkExperience
    {\textbf{Senior Software Engineer}}
    { \href{https://www.vimeo.com}{\textbf{Vimeo}} }
    {Jan 2024 - Jan 2026}
    {Remote, India}
    {
      \item[$\bullet$] \textbf{Strategic Compliance (Age Assurance):} Led cross-platform compliance strategy for \textbf{4.5M+ users} under the \textbf{UK Online Safety Act} and EU DSA, mitigating revenue risks (10\% of global turnover). Engineered a \textbf{Zero-Trust architecture} that eliminates SPI persistence via vendor-edge filtering, reducing GDPR liability by \textbf{100\%}. Designed ``Exemption Workflows'' to bypass verification for premium users, safeguarding high-value revenue streams from churn.
      \item[$\bullet$] \textbf{Legacy Modernization Architecture (Identity):} Designed the architectural blueprint for ``Anumati,'' a \textbf{Golang} microservice to decouple authentication from the legacy PHP monolith. Reverse-engineered 15 years of undocumented logic to map the \textbf{Strangler Pattern} migration strategy and implemented core pre/post-login flows to prepare for system decomposition.
      \item[$\bullet$] \textbf{Backend Scaling (User Deactivation Engine):} Re-architected the deactivation system using \textbf{Domain-Driven Design (DDD)} and \textbf{Asynchronous Queueing}. Scaled bulk processing capacity from 4K to \textbf{50K+ accounts} per batch, resolving HTTP timeouts. Reduced processing time by \textbf{99.9\%} (2 days to under 5 mins) and reconciled \textbf{195K+} inconsistent records.
      \item[$\bullet$] \textbf{Security \& Observability:} Identified a critical MFA bypass flaw and \textbf{authored the design specification} for a Backup Recovery Code system. Hardened auth flows against XSS and Open Redirect vectors. Defined \textbf{SLOs}, instrumented Grafana dashboards achieving \textbf{0\%} data inconsistencies, and authored source-of-truth \textbf{technical specifications} for Compliance and Auth domains.
    }

\WorkExperience
    {\textbf{Engineer 2}}
    {\href{https://www.mckinsey.com/}{\textbf{McKinsey \& Company}} }
    {Nov 2021 - Jan 2024}
    {Bengaluru, India}
    {
      \item[$\bullet$] Architected \textbf{GenAI-powered backend services} for enterprise banking IVR, designing secure OpenAI integration layers with PII redaction and stateful conversation orchestration using \textbf{NestJS}.
      \item[$\bullet$] Built \textbf{event-driven medication adherence platform} using \textbf{Azure Functions and Twilio}, implementing fault-tolerant message routing and scheduling flows with \textbf{HIPAA-compliant} healthcare data handling at scale.
      \item[$\bullet$] Optimized \textbf{NestJS microservices} serving \textbf{500K+ monthly users}, reducing API response times by \textbf{50\%} through caching and index optimization. Led architecture reviews, mentored 4 engineers, established API design standards, and drove CI/CD adoption across teams.
    }

\WorkExperience
    {\textbf{Engineer 1}}
    { \href{https://www.mckinsey.com/}{\textbf{McKinsey \& Company}} }
    {Jul 2018 - Nov 2021}
    {Bengaluru, India}
    {
      \item[$\bullet$] Designed \textbf{microservices architecture} for Malaysian banking self-service platform serving \textbf{20M+ customers}, decomposing legacy SOAP integrations into \textbf{REST-based services}. Increased relationship manager productivity by \textbf{60\%} through workflow automation and API modernization.
      \item[$\bullet$] Developed \textbf{insurance recommendation engine} for \textbf{1.3M users} using React and Node.js, improving operational efficiency by \textbf{90\%}. Built telecom customer platforms for \textbf{10M users}, increasing test coverage by \textbf{40\%} and strengthening session management reliability.
    }

\section{\textcolor{NavyBlue}{Education}}

\EducationExperience
    {Vellore Institute of Technology}
    {\textbf{Bachelor of Technology}, Information Technology}
    {2018}
    {Vellore, India}

\section{\textcolor{NavyBlue}{Skills}}

\SkillList{
    \SkillItem{Open Source}{: Contributed to \href{https://github.com/apple/password-manager-resources/pull/1019}{\textbf{Apple}/password-manager-resources}, \href{https://github.com/transferwise/pipelinewise/pull/1263}{\textbf{Wise}/PipelineWise}, \href{https://github.com/amruthpillai/reactive-resume/pull/1978}{Reactive Resume} (PRs merged)}
    \SkillItem{Languages}{: JavaScript, TypeScript, SQL; \textbf{Familiar:} Go (Golang), PHP, Java, Python}
    \SkillItem{Frontend}{: React, Next.js, Tailwind, Web Security (CSP/XSS), Jest}
    \SkillItem{Backend}{: Node.js, NestJS, Express.js; \textbf{Familiar:} Spring Boot, FastAPI}
    \SkillItem{Databases}{: PostgreSQL, MySQL, Redis, MongoDB; TypeORM}
    \SkillItem{Cloud \& DevOps}{: Docker, GitHub Actions, CircleCI; \textbf{Familiar:} AWS, Azure, GCP, Kubernetes, Grafana}
    \SkillItem{Architecture}{: Microservices, DDD, Event-Driven, REST, GraphQL, gRPC, OAuth 2.0, Async Processing, Message Queues}
}

\end{document}