\vspace{-2.6mm}
\cvsection{Projects}
\begin{cvprojectentries}
\vspace{-1mm}
  \cvprojectentry
    {\href{https://shubhammathur.me/MovieCataloger}{\color{darkred}Movie Cataloger}}
    {\small A desktop application in Java to manage personal movie collection. It finds movies on local storage and retrieves their data from IMDb. It supports categorization, graphical analysis and batch copying of movies.
    }
    \newline
  \cvprojectentry    
    {\href{https://shubhammathur.me/FragileWatermarking}{\color{darkred}Fragile Watermarking}}
    {\small Embedded and extracted watermark in images using LSB bit manipulation, compared images using PSNR, BER. The algorithms and complete GUI was developed in Java.
    }
    \newline
  \cvprojectentry    
    {\href{https://shubhammathur.me/PythonScripts}{\color{darkred}Web Crawler and scrappers}}
    {\small Collection of python scripts written which uses Selenium to crawl, scrap and save user's accepted submissions on HackerRank, LeetCode and on Campusinteraction, it scrapes data and generates SQL table about the companies that visited VIT for recruiting 2017 passing batch students.
    }
    \newline
  \cvprojectentry    
    {\href{https://shubhammathur.me/Value-Time}{\color{darkred}Value Time}}
    {\small A chrome extension to replace the default new tab with a web-page, showing time remaining in the day and motivational quotes, which keeps one motivated to complete their daily goals and prevent them to waste any time.
    }
    \newline
  \cvprojectentry    
    {\href{https://github.com/googleknight/jaipur-bus-app}{\color{darkred}Jaipur Bus Info}}
    {\small An android app to know bus stops, routes of local low floor government buses running in Jaipur city.
    }    
\end{cvprojectentries}
